Repeated loss of variation in insect ovary morphology highlights the role of developmental constraint in life-history evolution

### 2020-07-07 manuscript.Rmd
updating commit number

Samuel H Church^1^\*, Bruno A. S. de Medeiros^1,2^, Seth Donoughe^1,3^, Nicole L. Márquez Reyes^4^, Cassandra G. Extavour^1,5^\*

@@

The dataset of insect ovariole number is available in the supplementary file 'ovariole_number_data.tsv' and has been uploaded to Dryad (doi:10.5061/dryad.59zw3r253). The code and phylogenetic trees required to reproduce all the analyses, figures, and generate the manuscript files are provided at 'https://github.com/shchurch/insect_ovariole_number_evolution_2020'.

@@

![**The evolution of the presence and position of nurse cells.** a, Insect oogenesis was categorized into several modes by Büning[@buning1994insect] based on the presence and position of nurse cells. b, Phylogenetic reconstruction of mode of oogenesis. Scale bar indicates 100 million years (Myr). Gray = panoistic ovaries, without nurse cells, cyan=polytrophic meroistic ovaries, with nurse cells adjacent to maturing oocytes, red = telotrophic meroistic ovaries, with nurse cells located in germaria, black = unique meroistic ovary type observed in Strepsiptera. Insect taxonomic groups are, from top to bottom: Apterygota, Palaeoptera, Polyneoptera, Condylognatha, Psocodea, Hymenoptera, Neuropteroidea, Amphiesmenoptera, and Antliophora. ](manuscript_figures/Fig_Ovary_V8-01.png)

>>>>

Samuel H. Church^1^\*, Bruno A. S. de Medeiros^1,2^, Seth Donoughe^1,3^, Nicole L. Márquez Reyes^4^, Cassandra G. Extavour^1,5^\*

@@

The dataset of insect ovariole number is available in the supplementary file 'ovariole_number_data.tsv' and has been uploaded to Dryad (doi:10.5061/dryad.59zw3r253). The code and phylogenetic trees required to reproduce all the analyses, figures, and generate the manuscript files are provided at 'https://github.com/shchurch/insect_ovariole_number_evolution_2020', commit 6cf446a.

@@

![**The evolution of the presence and position of nurse cells.** a, Insect oogenesis was categorized into several modes by Büning[@buning1994insect] based on the presence and position of nurse cells. b, Phylogenetic reconstruction of mode of oogenesis. Scale bar indicates 100 million years (Myr). Gray = panoistic ovaries, without nurse cells, cyan = polytrophic meroistic ovaries, with nurse cells adjacent to maturing oocytes, red = telotrophic meroistic ovaries, with nurse cells located in germaria, black = unique meroistic ovary type observed in Strepsiptera. Insect taxonomic groups are, from top to bottom: Apterygota, Palaeoptera, Polyneoptera, Condylognatha, Psocodea, Hymenoptera, Neuropteroidea, Amphiesmenoptera, and Antliophora. ](manuscript_figures/Fig_Ovary_V8-01.png)
